Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-03-08 paper-1/manuscript.tex
Added F10 to manuscript

>>>>

\begin{figure*}%
    \centering
    \includegraphics{fig10.pdf}
    \caption{}
    \label{fig10}
\end{figure*}
\textbf{Fig. 9} Suppression acts in spatially distinguishable subpopulations.
\textbf{a} Response size $\R{A}{}$ as a function of distance from the center of the stimulation site, evaluated across all networks and stimuli in 200 bins between 0 mm and 6.5 mm, and normalized by the response size in recovered networks (initial trial). Each of the 200 data points represents the mean response across all relevant trials of all neurons in the corresponding distance bin. Left, spatial illustration, using all data with a fictive stimulus location. Right, same data plotted as lines. The vertical line indicates the chosen local/global divider.
\textbf{b} As in panel a, but showing $\T{A}{}$ without normalization.
\textbf{c} As in panel a, but showing $\D{A}{}$ without normalization.
\textbf{d} Mean $\T{A}{}$ in neurons <2 mm from the stimulation site (local) and more distant neurons (global). Data are averaged across relevant neurons and trials in each network and stimulus, leaving 120 data points to be summarized by box plot. Comparisons of interest are between \std{} and \dev{} in the local subset, and between \msc{} and \dev{} in the global subset.
\textbf{e} Corresponding mean $\D{A}{}$ in local and global portions of the network.
